# Easy.

```{r}
library(rethinking) # Needed starting at 3E6
p_grid <- seq(from=0, to=1, length.out=1000)
prior <- rep(1, 1000)
likelihood <- dbinom(6, size=9, prob=p_grid)
posterior <- likelihood * prior
posterior <- posterior / sum(posterior)
set.seed(100)
samples <- sample(p_grid, prob=posterior, size=1e4, replace=TRUE)
```

__3E1.__ How much posterior probability lies below _p_ = 0.2?

```{r}
sum(samples < 0.2) / 1e4
```

OR

```{r}
mean(samples < 0.2)
```    

__3E2.__ How much posterior probability lies above _p_ = 0.8?

```{r}
mean(samples > 0.8)
```

__SE3.__ How much posterior probability lies between _p_ = 0.2 and _p_ = 0.8?


```{r}
mean(samples > 0.2 & samples < 0.8)
```

__SE4.__ 20% of the posterior probability lies below which value of _p_?

```{r}
quantile(samples, 0.2)
```

__3E5.__ 20% of the posterior probability lies aboue which value of _p_?
```{r}
quantile(samples, 0.8)
```

__3E6.__ Which values of _p_ contain the narrowist interval equal to 66% of the posterior probability?

```{r}
HPDI(samples, prob=0.66)
```

__SE7.__ Which values of _p_ contain 66% of the posterior probability, assuming equal posterior probabilities both below and above the interval?

```{r}
PI(samples, prob=0.66)
```


## Medium.

__3M1.__ Suppose the globe tossing data had turned out to be 8 water in 15
tosses. Construct the posterior distribution,  using grid approximation. Use
the same flat prior as before.

```{r}
p_grid <- seq(0, 1, length.out=1000)
prior <- rep(1, 1000)
likelihood <- dbinom(8, 15, p_grid)
posterior <- likelihood * prior 
posterior <- posterior / sum(posterior)
```

__3M2.__ Draw 10,000 samples from the grid approximation from above. Then use
the samples to calculate the 90% HDPI for _p_.

```{r}
samples <- sample(p_grid, prob=posterior, size=1e4, replace=TRUE)
HPDI(samples, 0.9)
```

__3M3.__ Construct a posterior predictive check for this model and data. This means simulate the distribution of samples, averaging over the posterior uncertainty in p. What is the probability of observing 8 water in 15 tosses?

```{r}
ppd <- rbinom(1e4, size=15, prob=samples)
p_eight <- mean(ppd == 8)
p_eight
```

_3M4._ Using the posterior distribution constructed from the new (8/15) data,now calculate the probability of observing 6 water in 9 tosses.

Not sure based on the wording, but maybe this:
```{r}
ppd_nine <- rbinom(1e4, size=9, prob=samples)
p_six <- mean(ppd_nine == 6)
p_six
```
 
__3M5.__ Start over at 3M1, but now use a prior that is zero below p = 0.5 and a constant above p = 0.5.  is corresponds to prior information that a majority of the Earth’s surface is water. Repeat each problem above and compare the inferences. What di erence does the better prior make? If it helps, compare inferences (using both priors) to the true value p = 0.7.

```{r}
p_grid <- seq(0, 1, length.out=1000)
prior <- c(rep(0, 500), rep(2, 500))
likelihood <- dbinom(8, 15, p_grid)
posterior <- likelihood * prior
posterior <- posterior / sum(posterior)
samples <- sample(p_grid, prob=posterior, size=1e4, replace=TRUE)
HPDI(samples, 0.9)

ppd <- rbinom(1e4, size=15, prob=samples)
p_eight <- mean(ppd == 8)
p_eight

ppd_nine <- rbinom(1e4, size=9, prob=samples)
p_six <- mean(ppd_nine == 6)
p_six
```
